% Tim O'Brien CV/résumé ~ Feb 2018
%
% Adapted from moderncv template.tex
% Copyright 2006-2012 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[10pt,letterpaper,roman,final]{moderncv}
% possible options include font size ('10pt', '11pt' and '12pt'), paper size
% ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and
% 'landscape') and font family ('sans' and 'roman')


% ModernCV themes -------------------------------------------------------------
% Style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{banking}
% Color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey'
% and 'black'
\moderncvcolor{black}
% Name size
\renewcommand*{\namefont}{\fontsize{22}{26}\mdseries\upshape}
% \renewcommand*{\namefont}{\fontsize{22}{40}\mdseries\upshape}

% character encoding
\usepackage[utf8]{inputenc}

% Adjust the page margins
\usepackage[scale=0.84]{geometry}
\recomputelengths

% personal data
\firstname{Timothy}
\familyname{O'Brien}
% \address{3133 Frontera Way \#413}{Burlingame, CA 94010}
\address{3133 Frontera Way, Apt. 413, Burlingame, CA 94010}{}

\mobile{(917)~280-4532}
\email{tsob@ccrma.stanford.edu}
\homepage{ccrma.stanford.edu/\textasciitilde tsob}

% Remove emoji
\renewcommand*{\addresssymbol}       {}
\renewcommand*{\mobilephonesymbol}   {}
\renewcommand*{\fixedphonesymbol}    {}
\renewcommand*{\faxphonesymbol}      {}
\renewcommand*{\emailsymbol}         {}
\renewcommand*{\homepagesymbol}      {}
\renewcommand*{\linkedinsocialsymbol}{}
\renewcommand*{\twittersocialsymbol} {}
\renewcommand*{\githubsocialsymbol}  {}

%------------------------------------------------------------------------------
%            content
%------------------------------------------------------------------------------
\begin{document}
% Resume ----------------------------------------------------------------------
\makecvtitle
\vspace{-22px}

\section{Education} % ---------------------------------------------------------

\cventry
{Sep.\ 2014--\textit{present}}
{Ph.D.}
{Stanford University}
{Stanford, CA}
{\textit{Computer-Based Music Theory and Acoustics}}
{\begin{itemize}
   \item Research focuses on deep learning applied to musical applications.
         Advised by Prof.\ Julius O.\ Smith, III. All coursework completed.
   \item Helped develop and teach \textit{Music 421N: Deep Learning for
         Music and Audio}.
   \item Instructor for introductory computer music composition class;
         served as teaching assistant for six courses.
 \end{itemize}}

\cventry
{Sep.\ 2012--Apr.\ 2014}
{M.A.}
{Stanford University}
{Stanford, CA}
{\textit{Music, Science and Technology -- Center for Computer Research in Music
 and Acoustics}}
 \begin{itemize}
   \item GPA: 4.116
   \item Studies included digital signal processing, computer music
         composition, and human-computer interaction design.
   \item Research included complex system simulation for computer
         improvisation and real-time generative algorithmic composition.
   % \item GRE (\textit{September 2011}): 170 Verbal (99th percentile), 168
   %       Quantitative (96th percentile), 4.5 Analytical Writing (72nd
   %       percentile)
 \end{itemize}}

\cventry
{Aug.\ 2002--May 2006}
{B.S.}
{University of Virginia}
{Charlottesville, VA}
{\textit{Physics}}
{Distinguished major in physics, concentration in computational physics, and
 minor in anthropology.
 \begin{itemize}
   \item Studies included C/C++ programming for analysis and simulation of
         physical systems.
   \item Senior thesis examined the dynamics of shear transformation zones in
         amorphous solids via numerical simulation.
   % \item Dean's List: Spring 2003, Fall 2003, Spring 2004, Spring 2005.
 \end{itemize}}

\section{Work Experience} % ---------------------------------------------------

\cventry
{Jun. 2016--\textit{present}}
{Intern--R\&D Engineering}
{Shazam}
{Redwood City, CA}
{}
{\begin{itemize}
   \item Trained neural net to intelligently reduce network and server load
         with minimal user impact, leading to significant cost savings and
         increased reliability.
   \item Developed unsupervised ML system, leveraging a massive
         set of proprietary data, to characterize any song (\textit{e.g.}\ by
         genre).
 \end{itemize}}

\cventry
{May 2014--Aug.\ 2014}
{Intern--Audio Software Engineering}
{Apple}
{Cupertino, CA}
{}
{\begin{itemize}
   \item Developed an efficient solution to a user-facing audio
         interaction, leveraging the expertise and buy-in of multiple teams,
         which was deployed to millions of devices.
 \end{itemize}}

\cventry
{Jun.\ 2013--Sep.\ 2013}
{Intern--Audio DSP Engineering}
{Sennheiser Research}
{San Francisco, CA}
{}
{\begin{itemize}
   \item Developed object-oriented AutoMixer in Matlab, optimizing efficiency,
         agility, and ease of use.
   \item Researched DSP concepts, mainly compressed sensing; work included
         numerous Matlab experiments and simulations.
   \item Contributed to proprietary Matlab codebase, adhering to coding
         standards and guidelines.
 \end{itemize}}

\cventry
{Sep.\ 2006--Aug.\ 2012}
{Equity Research Assistant}
{J.P.\ Morgan Chase}
{New York, NY}
{}
{\begin{itemize}
   \item Partnered with department management to analyze expenses and make
         recommendations for expense savings; led training on new automated and
         web-based systems to achieve significant cost savings during the
         financial crisis.
   \item Identified and gathered key metrics for research publications and to
         fulfill client requests.
 \end{itemize}}

% \section{Musical Experience}
% \cventry{Summers 2003--2005, 2006--2012}{suiGeneris}{Bandleader}{New York, NY}{Limehead}{Composed, performed, and recorded original musical works as leader of a progressive, alternative metal group at numerous venues throughout New York City. U.S.\ finalist in the international Emergenza battle of the bands competition. Produced numerous studio recordings of original material. Selected performance venues: Webster Hall, The Bitter End, Fat Baby, Don Hill's, CBGB.}
% %\cventry{2010--2011}{Um}{Guitarist}{New York, New York}{Who's RVZ?}{Lead guitarist for Brooklyn and Manhattan-based indie rock band \textit{Um}; sole guitarist for \textit{Who's RVZ?}, performing deep cuts from Van Halen, Led Zeppelin, and The Who at venues in Manhattan and Queens, New York.}

\section{Additional}
\begin{itemize}
  \item Avid guitar player and composer.
  \item Lead guitarist for two alternative metal bands that performed original works at venues throughout New York City.
  % \item U.S. finalist in international Emergenza battle of the bands competition.
\end{itemize}

\section{Skills}
\begin{minipage}[t]{0.50\linewidth}
  \cvitem{Programming}{Python, C, C++, Matlab, \textit{etc.}}
  \cvitem{ML Libraries}{Keras, TensorFlow, PyTorch}
\end{minipage}
\begin{minipage}[t]{0.50\linewidth}
  \cvitem{DSP}{Audacity, Ardour, Faust, SuperCollider, PD, ChucK}
  \cvitem{Misc.}{Linux, Bash, Vim, Git}
  % \cvitem{Applications}{\textit{etc.}}
  % \cvitem{Web Technologies}{HTML, CSS, Jekyll, Pelican}
\end{minipage}



\end{document}
